\documentclass[12pt,a4paper]{report}

% Packages
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\usepackage[hidelinks]{hyperref}
\usepackage{amsmath}
\usepackage{setspace}
\usepackage{fancyhdr}

\onehalfspacing

% Header & Footer
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{Service Management System}
\fancyhead[R]{Project Documentation}
\fancyfoot[C]{\thepage}

\begin{document}

%---------------------------------------
% Title Page
%---------------------------------------

\begin{titlepage}
\centering

\vspace*{2cm}

{\Huge \textbf{Service Management System}}\\[0.5cm]
{\Large Project Documentation}

\vspace{2cm}

\textbf{Author:} \\
[0.3cm]
Your Name

\vspace{1cm}

\textbf{Institution / Organization}

\vspace{1cm}

\textbf{Date:} \today

\vfill

\end{titlepage}

%---------------------------------------
% Table of Contents
%---------------------------------------

\pagenumbering{roman}
\tableofcontents
\newpage

\pagenumbering{arabic}

%---------------------------------------
\chapter{Introduction}

\section{Problem Description}

Managing service operations manually presents several challenges such as inefficiencies in booking service appointments, tracking service jobs, and maintaining customer and vehicle records.

\section{Existing System Analysis}

Existing systems rely on manual processes which lead to:

\begin{itemize}
\item Lack of integration between departments
\item Slow data retrieval
\item Human errors in documentation
\item Poor tracking of service history
\end{itemize}

\section{Project Scope}

The Service Management System integrates:

\begin{itemize}
\item Backend APIs
\item Frontend interface
\item Database management
\item Test ride management
\item Role-based system access
\end{itemize}

\section{Objectives}

\begin{itemize}
\item Streamline service operations
\item Implement role-based access control
\item Enable efficient CRUD operations
\item Manage test ride bookings and conversions
\end{itemize}

%---------------------------------------
\chapter{Customer Differentiation}

\section{New Customers}

New customers are individuals registering in the system for the first time. The workflow includes:

\begin{enumerate}
\item Register customer personal details
\item Register vehicle details
\item Create service job cards
\end{enumerate}

\section{Existing Customers}

Existing customers already have records stored in the system. Their workflow includes:

\begin{enumerate}
\item Retrieve customer profile
\item Retrieve vehicle details
\item Create new job cards or view service history
\end{enumerate}

\section{Test Ride Customers}

Test ride customers are potential buyers visiting the showroom for vehicle trials.

These customers may later convert into regular customers if they proceed with a purchase or service.

%---------------------------------------
\chapter{Test Ride Management}

\section{Test Ride Booking}

The system allows scheduling test rides by collecting:

\begin{itemize}
\item Customer details
\item Vehicle preference
\item Test ride date and time
\end{itemize}

\section{Feedback Collection}

After the test ride, feedback is collected regarding:

\begin{itemize}
\item Vehicle performance
\item Customer experience
\item Purchase interest
\end{itemize}

\section{Follow-Up Process}

The system enables follow-ups for customers who show interest after test rides.

\section{Conversion to Regular Customer}

Test ride customers can be converted into regular customers if they proceed with a purchase or service.

%---------------------------------------
\chapter{System Analysis}

\section{Architecture Overview}

The system follows a client-server architecture consisting of:

\begin{itemize}
\item Frontend interface built using React
\item Backend APIs developed using Node.js and Express
\item Database managed through Prisma ORM
\end{itemize}

\section{Functional Specifications}

\subsection{User Stories}

Example user story:

\textit{As a service advisor, I want to create a job card so that I can track service details.}

\subsection{Use Case Details}

Main system use cases include:

\begin{itemize}
\item Create job card
\item Manage customers
\item Manage vehicles
\item Schedule test rides
\item Collect customer feedback
\end{itemize}

\section{System Requirements}

\subsection{Functional Requirements}

\begin{itemize}
\item Role-based authentication
\item CRUD operations
\item Email notifications
\item File uploads
\item Test ride management
\end{itemize}

\subsection{Non-Functional Requirements}

\begin{itemize}
\item Security
\item Scalability
\item Reliability
\end{itemize}

%---------------------------------------
\chapter{Role-Based Access Control}

\section{Admin}

Admin users can:

\begin{itemize}
\item Manage users
\item View all job cards
\item Manage test ride bookings
\item Access reports and analytics
\end{itemize}

\section{Service Advisor}

Service advisors can:

\begin{itemize}
\item Register customers
\item Create job cards
\item Schedule test rides
\end{itemize}

\section{Technician}

Technicians can:

\begin{itemize}
\item View assigned job cards
\item Update service status
\end{itemize}

\section{Customer}

Customers can:

\begin{itemize}
\item Book test rides
\item Provide feedback
\item Track service status
\end{itemize}

%---------------------------------------
\chapter{System Design}

\section{Architecture Design}

The system architecture consists of three main layers:

\begin{itemize}
\item Frontend Layer
\item Backend API Layer
\item Database Layer
\end{itemize}

\section{Data Flow Diagram}

The data flow diagram illustrates communication between the user interface, backend services, and database.

\section{Database Schema}

Main database entities include:

\begin{itemize}
\item Customers
\item Vehicles
\item Job Cards
\item Service Records
\item Test Rides
\end{itemize}

\subsection{Test Ride Table}

The \texttt{test\_rides} table stores:

\begin{itemize}
\item Booking ID
\item Customer details
\item Vehicle preference
\item Test ride schedule
\item Feedback
\item Conversion status
\end{itemize}

%---------------------------------------
\chapter{Implementation}

\section{Technology Stack}

\begin{itemize}
\item Backend: Node.js, Express, Prisma ORM
\item Frontend: React, Vite, TailwindCSS
\item Database: SQL-based cloud database
\end{itemize}

\section{Key Features}

\subsection{CRUD Operations}

Create, update, read, and delete operations for customers, vehicles, and job cards.

\subsection{Role-Based Access}

Admin and staff roles control system access.

\subsection{Email Notifications}

Automated notifications for service updates and bookings.

\subsection{File Uploads}

Support for uploading service-related files.

\section{Admin Dashboard Features}

The admin dashboard includes:

\begin{itemize}
\item Job card management
\item Test ride booking management
\item Customer management
\item Service status tracking
\end{itemize}

Example dashboard table columns:

\textbf{Job Cards Table}

\begin{itemize}
\item Job Card ID
\item Customer Name
\item Vehicle Model
\item Service Type
\item Status
\item Actions
\end{itemize}

\textbf{Test Ride Table}

\begin{itemize}
\item Booking ID
\item Customer Name
\item Vehicle Preference
\item Test Ride Date
\item Feedback
\item Status
\item Actions
\end{itemize}

\section{Color-Coded Statuses}

The system uses color-coded statuses:

\textbf{Job Cards}

\begin{itemize}
\item Open -- Yellow
\item In Progress -- Blue
\item Completed -- Green
\end{itemize}

\textbf{Test Rides}

\begin{itemize}
\item Scheduled -- Blue
\item Completed -- Green
\item Cancelled -- Red
\end{itemize}

%---------------------------------------
\chapter{Testing}

\section{Testing Strategy}

\subsection{Unit Testing}

Testing of individual modules.

\subsection{Integration Testing}

Ensures interaction between frontend and backend.

\subsection{System Testing}

Full system functionality testing.

\section{Test Reports}

Performance metrics and bug reports are documented.

%---------------------------------------
\chapter{Deployment}

\section{Deployment Architecture}

The application is deployed on cloud infrastructure where frontend, backend, and database operate on separate services.

\section{Deployment Checklist}

\subsection{Pre-Deployment}

\begin{itemize}
\item Configure environment variables
\item Run database migrations
\item Seed database
\end{itemize}

\subsection{Post-Deployment}

\begin{itemize}
\item Verify APIs
\item Test authentication
\item Monitor system logs
\end{itemize}

%---------------------------------------
\chapter{User Guides}

\section{Admin Dashboard Quick Start}

\begin{enumerate}
\item Login to the system
\item Navigate to dashboard
\item Create job cards or test ride bookings
\item Monitor service operations
\end{enumerate}

\section{FAQ}

\textbf{Q: How do I differentiate between new and existing customers?}

New customers must be registered first, while existing customers can be retrieved from stored records.

\textbf{Q: How can I schedule a test ride booking?}

Navigate to the Test Ride section in the dashboard and schedule the booking.

\textbf{Q: How can a test ride customer be converted to a regular customer?}

Use the conversion option available in the Test Ride Management section.

%---------------------------------------
\chapter{Conclusion}

\section{Future Enhancements}

\begin{itemize}
\item Automated follow-ups for test ride customers
\item Analytics for test ride conversions
\item Advanced reporting dashboards
\item System scalability improvements
\end{itemize}

\section{Lessons Learned}

This project provided experience in full-stack development, system architecture design, API integration, and database management.

\chapter{References}

\begin{itemize}
\item Node.js Documentation
\item Prisma Documentation
\item React Documentation
\item TailwindCSS Documentation
\end{itemize}

\end{document}